---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covid

<!-- badges: start -->
[![R build status](https://github.com/etc5523-2020/r-package-assessment-cgon0007/workflows/R-CMD-check/badge.svg)](https://github.com/etc5523-2020/r-package-assessment-cgon0007/actions)
<!-- badges: end -->

The goal of covid_tracker is to provid the covid-19 data and function for the people to explore.

## Installation

You can install the released version of covid_tracker from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("covid")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-cgon0007")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(covid)
library(tibble)
coronavirus
n_countries(coronavirus)
## basic example code
```

## shiny part

User can choose to run shinyChromosome installed on local computers (Windows, Mac or Linux) for a more preferable experience.
hint(the app means that:covid19-tracker-shinyapp)
Step 1: Install R and RStudio

Before running the app you will need to have R and RStudio installed (tested with R 3.5.0 and RStudio 1.1.419).
Please check CRAN (https://cran.r-project.org/) for the installation of R.
Please check https://www.rstudio.com/ for the installation of RStudio.

Step 2: Install the R Shiny package and other packages required by shinyChromosome

Start an R session using RStudio and run these lines:

### try an http CRAN mirror if https CRAN mirror doesn't work


`install.packages("shiny")`
`install.packages("ggplot2")`
`install.packages("shinythemes")`
`install.packages("coronavirus")`

### install shiny:covid_tracker 

`install.packages("devtools") ` 
`devtools::install_github("~cgon0007/app", force=TRUE) ` 

Step 3: Start the app

Start an R session using RStudio and run these lines:


`shiny::runGitHub("app", "cgon0007")`

This command will download the code of shinyapp from GitHub to a temporary directory of your computer and then launch the app in the web browser. Once the web browser was closed, the downloaded code of app would be deleted from your computer. Next time when you run this command in RStudio, it will download the source code of appcovid19tracker from GitHub to a temporary directory again. This process is frustrating since it takes some time to download the code of shinyChromosome from GitHub.

Users are suggested to download the source code of shinyChromosome from GitHub to a fixed directory of your computer, such as 'E:\apps' on Windows.a zip file named 'app-master.zip' would be downloaded to the disk of your computer. Move this file to 'E:\apps' and unzip this file. Then a directory named 'app' would be generated in 'E:\apps'. 

Then you can start the app by running these lines in RStudio.


`library(shiny)`
`runApp("E:/apps/app-master", launch.browser = TRUE)`












