---
title: "the coronavirus dataset"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{the coronavirus dataset}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



```{r setup}
library(covid)
library(ggplot2)
library(dplyr)
```
# DESCRIPTION
this data contain 2000960 observations and 9 variables.
Docs: data ,data_type ,lat ,location ,location_code ,location_code_type,location_type,long ,value.
@description the covid-19 dataset, and some function can help people to understand and explore this illness

 @format A data frame with 9 variables
 
**data**:the data
- **data_type**:Data in Yyy
 -**lat**:Latitude of center of geographic region, defined as either
 country or, if available, province
 -**location**Name of province/state, for countries where data is
  provided split across multiple provinces/states   
  -**location_code**:Name of country/region
  -**location_code_type**:the type of location
 -**location_type**:country
 -**long**:Longitude of center of geographic region, defined as either
  country or, if available, province
  -**value**Number of cases on given date
 @source Johns Hopkins University Center for Systems Science and Engineering
(JHU CCSE) Coronavirus \href{https://systems.jhu.edu/research/public-health/ncov/}{website}.
 @keywords datasets coronavirus COVID19
 @details The dataset contains the daily summary of Coronavirus cases
(confirmed, death, and recovered), by state/province.
# plot 
```{r}
conf_df <- coronavirus %>% 
  filter(data_type == "cases_new") %>%
  group_by(location) %>%
  summarise(total_cases = sum(value)) %>%
  arrange(-total_cases) %>%
  head( 10)

 library(ggplot2)
ggplot(conf_df,aes(x=location,y=total_cases,fill=location))+
  geom_bar(stat = "identity", alpha = 0.7) + 
  coord_polar()+
  theme(panel.border=element_blank())  

```

```{r}
conf_df1 <- coronavirus %>% 
  filter(data_type == "deaths_new") %>%
  group_by(location) %>%
  summarise(deaths = sum(value)) %>%
  arrange(-deaths) %>%
  head( 10)

 library(ggplot2)
ggplot(conf_df1,aes(x=location,y=deaths,fill=location))+
  geom_bar(stat = "identity", alpha = 0.7) + 
  coord_polar()+
  theme(panel.border=element_blank())  

```
```{r}
conf_df2 <- coronavirus %>% 
  filter(data_type == "recovered_new") %>%
  group_by(location) %>%
  summarise(recovered = sum(value)) %>%
  arrange(-recovered) %>%
  head( 10)

 library(ggplot2)
ggplot(conf_df2,aes(x=location,y=recovered,fill=location))+
  geom_bar(stat = "identity", alpha = 0.7) + 
  coord_polar()+
  theme(panel.border=element_blank())  
```












